\pkg{NeuralNetTools}: Visualization and Analysis Tools for Neural Networks

### 2015-10-11 nnt_manu.Rnw
link to flight imp code

The effects of network architecture and initial starting weights on indications of variable importance were evaluated by creating a large number of models and assessing the uncertainty of the importance measures.  Models with one, five, or ten hidden nodes and 100 separate models for each node level with a different set of random starting weights were evaluated.  The relative importance of the variables was saved for each model and combined in a single plot to show overall variable importance as the median and 5\textsuperscript{th}/95\textsuperscript{th} percentiles from the 100 models for each node level (get \href{code}{}).

>>>>

The effects of network architecture and initial starting weights on indications of variable importance were evaluated by creating a large number of models and assessing the uncertainty of the importance measures.  Models with one, five, or ten hidden nodes and 100 separate models for each node level with a different set of random starting weights were evaluated.  The relative importance of the variables was saved for each model and combined in a single plot to show overall variable importance as the median and 5\textsuperscript{th}/95\textsuperscript{th} percentiles from the 100 models for each node level (get \href{https://raw.githubusercontent.com/fawda123/nnt_manu/master/flightimp.R}{code}).
